---
title: "Group 5: Table manners and epidemics"
author: 
- Egydio Pacheco Neto
- Fabio Baldivia Pohl
- Gabriel Eduardo Moyano
- Giovana Oshiro da Silva
- Norma Rocio Forero Muñoz
- Raul Ossada
- Rodrigo Malavazi Corder
date: "2018 January 18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Link to Github Repository: https://github.com/raulossada/ift_2018

# 1 INTRODUCTION

It is very difficult to pronounciate Zoochlorella. (guestimate)

Zoochlorella are algae.

Paramecium is a cilliate protist.

Paramecium endosymbiosis with Zoochlorella.

Didinium is a specialist predator of Paramecium. Messy Feeding and Full Feeding

Chlorovirus is a large DNA, that can't attack Zoochlorellas that are inside a Paramecium

# 2 MATERIALS AND METHODS

## 2.1 Model Hipothesis

What we didn't include?

1) Due to the high growth rate of Zoochlorella inside of a Paramecium we assume that this population reaches its maximum

2) Handling Time (Didinium is a voracious predator)


What we included?

A) Logistic growth rates

B) Didinium is a specific predator

C) Increased chance for a Chorovirus attached to the membrane of a Paramecium to infect a Zoochlorella that was inside it

D) Messy feeding effect due larger size of Paramecium with Zoochlorella

E) Endosymbiosis between Zoochlorella and Paramecium

## 2.2 Equations

\begin{align*} 
\frac{dZ}{dt}&=r_{Z} Z \left(1-\frac{Z}{K_{Z}}\right) + (1-\alpha) g (w D + m_{P_{Z}}) P_{Z} - s Z P - i Z C \\ 
\frac{dP}{dt}&=r_{P} P \left(1-\frac{P}{K_{P}}\right) - h s Z P - u j P D \\
\frac{dP_{Z}}{dt}&=r_{P_{z}} P_{z} \left(1-\frac{P_{Z}}{K_{P_{Z}}}\right) + h s Z P - j P_{Z} D \\
\frac{dD}{dt}&=e j (u P + P_{Z}) D - m_{D} D \\
\frac{dC}{dt}&=b i Z C + b \alpha g (w D + m_{P_{Z}}) P_{Z} C - m_{C} C
\end{align*}


## 2.3 Numerical Aproximation

```{r, simulation, message=FALSE}
# libraries
library('deSolve');
library('reshape2');
library('ggplot2');
library('ggthemes');
library('scales');

# time sequence 
time <- seq(from=0, to=300, by=0.01);

# parameters
parameters <- c(r_Z=0.9, 
                r_P=0.6, 
                r_Pz=0.9, 
                K_z=5000,
                K_P=1000, 
                K_Pz=1200, 
                m_Pz=0.001, 
                m_D=0.4, 
                m_C=0.6,
                s=0.6, 
                i=0.05, 
                e=0.2, 
                j=0.01, 
                q=0.3,
                g=500, 
                alpha=0, 
                h=0.1, 
                b=1, 
                u=1);

# m1 = q*p
# m2+f2 = p
# m1+f1= p
# , 
# m1=0.75, 
# m2=0.30, 
# f1=0.25, 
# f2=0.70

# model
model1 <- function(t, state, parameters){
  with( as.list( c(state, parameters) ), {
    
    w <- q*j;
    dZ  <- r_Z*Z*(1-Z/K_z) + (1-alpha)*g*(w*D + m_Pz)*Pz - s*Z*P - i*Z*C;
    dP  <- r_P*P*(1-P/K_P) - h*s*Z*P - (u*j)*P*D;
    dPz <- r_Pz*Pz*(1-Pz/K_Pz) + h*s*Z*P - (j)*Pz*D;
    dD  <- e*j*( u*P + Pz )*D - m_D*D;
    dC  <- b*i*Z*C + b*alpha*g*(w*D + m_Pz)*Pz*C - m_C*C;
    
    return( list( c(dZ, dP, dPz, dD, dC) ) );
  })
}

# initial conditions
state <- c(Z=10, P=10, Pz=0, D=1, C=1);

# Numerical solution
res <- ode(y=state, times=time, func=model1, parms=parameters, method='lsoda');
```

\newpage
# 3 RESULTS

```{r, plot_base}
# Plot
res_df <- as.data.frame(x=res);
res_m <- melt(data=res_df, id.vars='time');
```

### Plot of all populations
```{r, plot_all, fig.align='center'}
p <- ggplot(data=res_m, mapping=aes(x=time, y=value, color=variable ) ) + 
  geom_point(size=0.5) + 
  scale_color_manual(breaks=c("Z", "P", "Pz", "D", "C"), values=c("green", "orange", "blue", "purple", "red") ) + 
  labs(y='Populations', color='Pop');
print(p);
```

\newpage
### Plot of the Zoochlorella Population
```{r, plot_Z, fig.align='center'}
Z_m <- res_m[which(res_m$variable=='Z'), ];
p_Z <- ggplot(data=Z_m, mapping=aes(x=time, y=value) ) + 
  geom_point(size=0.5, col='green') + 
  labs(y='Number of Zoochlorella (Z)');
print(p_Z);
```

\newpage
### Plot of the Paramecium Population
```{r, plot_P, fig.align='center'}
P_m <- res_m[which(res_m$variable=='P'), ];
p_P <- ggplot(data=P_m, mapping=aes(x=time, y=value) ) + 
  geom_point(size=0.5, col='orange') + 
  labs(y='Number of Paramecium spp (P)');
print(p_P);
```

\newpage
### Plot of the Paramecium with Zoochlorella Population
```{r, plot_Pz, fig.align='center'}
Pz_m <- res_m[which(res_m$variable=='Pz'), ];
p_Pz <- ggplot(data=Pz_m, mapping=aes(x=time, y=value) ) + 
  geom_point(size=0.5, col='blue') + 
  labs(y='Number of Paramecium spp with Zoochlorella (Pz)');
print(p_Pz);
```

\newpage
### Plot of the Didinium Population
```{r, plot_D, fig.align='center'}
D_m <- res_m[which(res_m$variable=='D'), ];
p_D <- ggplot(data=D_m, mapping=aes(x=time, y=value) ) + 
  geom_point(size=0.5, col='purple') + 
  labs(y='Number of Didinium nasutum (D)');
print(p_D);
```

\newpage
### Plot of the Chlorovirus Population
```{r, plot_C, fig.align='center'}
C_m <- res_m[which(res_m$variable=='C'), ];
p_C <- ggplot(data=C_m, mapping=aes(x=time, y=value) ) + 
  geom_point(size=0.5, col='red') + 
  labs(y='Number of Chlorovirus (C)');
print(p_C);
```

# 4 DISCUSSION

# 5 CONCLUSIONS

# 6 REFERENCES
[1] DeLong J. P., Al-Ammedi Z., Lyon S., Van Etten J. L. and Dunigan D. D. [Size-dependent catalysis of Chlorovirus population growth by a messy feeding predator](https://link.springer.com/article/10.1007%2Fs00248-017-1106-8). Microbial Ecology, November 2017.

[2] Cáceres C. E., Knight C. J. and Hall S. R. [Predator-spreaders: predation can enhance parasite success in a planktonic host-parasite system](http://onlinelibrary.wiley.com/doi/10.1890/08-2154.1/abstract). Ecology, 2009.



\newpage
# Appendix A


## Silly simulation 1
```{r, ap1}
# initial conditions
state <- c(Z=0, P=0, Pz=0, D=0, C=0);
```

```{r, ap1_plot, fig.align='center', echo=FALSE}
# Numerical solution
res <- ode(y=state, times=time, func=model1, parms=parameters, method='lsoda');

# Plot
res_df <- as.data.frame(x=res);
res_m <- melt(data=res_df, id.vars='time');

p <- ggplot(data=res_m, mapping=aes(x=time, y=value, color=variable ) ) + 
  geom_point(size=0.5) +
  scale_color_manual(breaks=c("Z", "P", "Pz", "D", "C"), values=c("green", "orange", "blue", "purple", "red") ) + 
  labs(y='Populations', color='Pop');
print(p);
```



## Silly simulation 2
```{r, ap2}
# initial conditions
state <- c(Z=1, P=0, Pz=0, D=0, C=0);
```
```{r, ap2_plot, fig.align='center', echo=FALSE}
# Numerical solution
res <- ode(y=state, times=time, func=model1, parms=parameters, method='lsoda');

# Plot
res_df <- as.data.frame(x=res);
res_m <- melt(data=res_df, id.vars='time');

p <- ggplot(data=res_m, mapping=aes(x=time, y=value, color=variable ) ) + 
  geom_point(size=0.5) +
  scale_color_manual(breaks=c("Z", "P", "Pz", "D", "C"), values=c("green", "orange", "blue", "purple", "red") ) + 
  labs(y='Populations', color='Pop');
print(p);
```



## Silly simulation 3
```{r, ap3}
# initial conditions
state <- c(Z=0, P=1, Pz=0, D=0, C=0);
```
```{r, ap3_plot, fig.align='center', echo=FALSE}
# Numerical solution
res <- ode(y=state, times=time, func=model1, parms=parameters, method='lsoda');

# Plot
res_df <- as.data.frame(x=res);
res_m <- melt(data=res_df, id.vars='time');

p <- ggplot(data=res_m, mapping=aes(x=time, y=value, color=variable ) ) + 
  geom_point(size=0.5) +
  scale_color_manual(breaks=c("Z", "P", "Pz", "D", "C"), values=c("green", "orange", "blue", "purple", "red") ) + 
  labs(y='Populations', color='Pop');
print(p);
```

## Silly simulation 4
```{r, ap4}
# initial conditions
state <- c(Z=0, P=0, Pz=1, D=0, C=0);
```
```{r, ap4_plot, fig.align='center', echo=FALSE}
# Numerical solution
res <- ode(y=state, times=time, func=model1, parms=parameters, method='lsoda');

# Plot
res_df <- as.data.frame(x=res);
res_m <- melt(data=res_df, id.vars='time');

p <- ggplot(data=res_m, mapping=aes(x=time, y=value, color=variable ) ) + 
  geom_point(size=0.5) +
  scale_color_manual(breaks=c("Z", "P", "Pz", "D", "C"), values=c("green", "orange", "blue", "purple", "red") ) + 
  labs(y='Populations', color='Pop');
print(p);
```

## Silly simulation 5
```{r, ap5}
# initial conditions
state <- c(Z=0, P=0, Pz=0, D=1, C=0);
```
```{r, ap5_plot, fig.align='center', echo=FALSE}
# Numerical solution
res <- ode(y=state, times=time, func=model1, parms=parameters, method='lsoda');

# Plot
res_df <- as.data.frame(x=res);
res_m <- melt(data=res_df, id.vars='time');

p <- ggplot(data=res_m, mapping=aes(x=time, y=value, color=variable ) ) + 
  geom_point(size=0.5) +
  scale_color_manual(breaks=c("Z", "P", "Pz", "D", "C"), values=c("green", "orange", "blue", "purple", "red") ) + 
  labs(y='Populations', color='Pop');
print(p);
```

## Silly simulation 6
```{r, ap6}
# initial conditions
state <- c(Z=0, P=0, Pz=0, D=0, C=1);
```
```{r, ap6_plot, fig.align='center', echo=FALSE}
# Numerical solution
res <- ode(y=state, times=time, func=model1, parms=parameters, method='lsoda');

# Plot
res_df <- as.data.frame(x=res);
res_m <- melt(data=res_df, id.vars='time');

p <- ggplot(data=res_m, mapping=aes(x=time, y=value, color=variable ) ) + 
  geom_point(size=0.5) +
  scale_color_manual(breaks=c("Z", "P", "Pz", "D", "C"), values=c("green", "orange", "blue", "purple", "red") ) + 
  labs(y='Populations', color='Pop');
print(p);
```
